greta.Rmd

### 2019-08-15 notebook/ghost-fit-forecast.Rmd
a few additional explorations

```{r}
data <- read_csv("../data/reps.csv.xz") # %>% filter(t %in% seq(0,4000, by=4))
data %>% ggplot(aes(t,x, group=reps)) + geom_line(alpha=0.02)
```

@@

lows <- means %>% dplyr::slice(1:10) %>% pull(reps)
highs <- means %>% dplyr::slice((n()-9):n()) %>% pull(reps)
coding <- function(reps) case_when(
  reps %in% lows ~ "low",
  reps %in% highs ~ "high"
)
extremes <- data %>% mutate(coding = coding(reps)) %>% na.omit()

write_csv(data.frame(lows=lows,highs=highs), "../data/extremes.csv.xz")
extremes %>% ggplot(aes(t, x, group=reps, color = coding)) + geom_line(alpha=0.5)

@@

```{r}
samples %>% ggplot() + 
  geom_histogram(aes(value), bins = 30)  +
  geom_vline(data = true, aes(xintercept = value), col = "red", lwd = 1) + 
  facet_wrap(~variable, scales = "free")
```

@@

samples2 %>% ggplot() + 
  geom_histogram(aes(value), bins = 30)  +
  geom_vline(data = true, aes(xintercept = value), col = "red", lwd = 1) + 
  facet_wrap(~variable, scales = "free")
```

@@

samples3 %>% ggplot() + 
  geom_histogram(aes(value), bins = 30)  +
  geom_vline(data = true, aes(xintercept = value), col = "red", lwd = 1) + 
  facet_wrap(~variable, scales = "free")
```

>>>>

```{r}
data <- read_csv("../data/reps.csv.xz") %>% filter(t < 2000)
data %>% ggplot(aes(t,x, group=reps)) + geom_line(alpha=0.02)
```

@@

lows <- means %>% dplyr::slice(1:10) %>% pull(reps)
highs <- means %>% dplyr::slice((n()-9):n()) %>% pull(reps)
write_csv(data.frame(lows=lows,highs=highs), "../data/extremes.csv.xz")

coding <- function(reps) case_when(
  reps %in% lows ~ "low",
  reps %in% highs ~ "high"
)
data %>% 
  mutate(coding = coding(reps)) %>% 
  na.omit() %>% 
ggplot(aes(t, x, group=reps, color = coding)) + geom_line(alpha=0.5)

@@

```{r}
samples %>% ggplot() + 
  geom_histogram(aes(value), bins = 30)  +
  geom_vline(data = true, aes(xintercept = value), col = "red", lwd = 1) + 
  facet_wrap(~variable, scales = "free")

write_csv(samples, "../data/posterior_highs.csv.xz")

@@

samples2 %>% ggplot() + 
  geom_histogram(aes(value), bins = 30)  +
  geom_vline(data = true, aes(xintercept = value), col = "red", lwd = 1) + 
  facet_wrap(~variable, scales = "free")

write_csv(samples2, "../data/posterior_lows.csv.xz")
```

@@

samples3 %>% ggplot() + 
  geom_histogram(aes(value), bins = 30)  +
  geom_vline(data = true, aes(xintercept = value), col = "red", lwd = 1) + 
  facet_wrap(~variable, scales = "free")

write_csv(samples3, "../data/posterior_ensemble.csv.xz")
```
